---
title: "Cao_Xiping_AssignmentV"
author: "Xiping Cao"
date: "2/2/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

#### Setting up a new GitHub repository
My project repository: https://github.com/cxp0330/AssignmentV.git

####Interacting with the API - the basics
```{r message=FALSE}
#load packages
rm(list = ls())

library(jsonlite)
library(httr)
library(rlist)
library(tidyverse)
library(naniar)
library(dplyr)

# set working directory:
#setwd("")
```

#### Interacting with the API - the basics
```{r message=FALSE}
# set API key
#APIkey <- "7elxdku9GGG5k8j0Xm8KWdANDgecHMV0"
source("Cao_Xiping_AssignmentV.R")

# get information from API
DE_Venues1 <- GET("https://app.ticketmaster.com/discovery/v2/venues",
                    query =list(apikey = APIkey,
                                locale = "*",
                                countryCode = "DE")) 

# extract all content and convert into a data frame
DE_Venues1_content <- fromJSON(rawToChar(DE_Venues1$content))
DE_Venues1_table <- as_tibble(DE_Venues1_content[["_embedded"]][["venues"]])

# extract specific content
DE_Venues1_table <- tibble(name = DE_Venues1_table$name,
                        city = DE_Venues1_table$city$name,
                        postalCode = DE_Venues1_table$postalCode,
                        address = DE_Venues1_table$address$line1,
                        url = DE_Venues1_table$url,
                        longitude = as.numeric(DE_Venues1_table$location$longitude),
                        latitude = as.numeric(DE_Venues1_table$location$latitude))

# take a look at the extracted information
glimpse(DE_Venues1_table)
```

#### Interacting with the API - advanced
The response only shows information about the first 20 venues. The size of each page is 20 and the "page" default setting of GET function is zero.
```{r}
# how much pages left to extracting information
pages <- as.numeric(DE_Venues1_content[["page"]][["totalPages"]])

# generate a list to store each page's information using a for loop
DE_Venues2_table <- list()
for (i in 1:pages) {
DE_Venues2 <- GET("https://app.ticketmaster.com/discovery/v2/venues",
                    query =list(apikey = APIkey,
                                locale = "*",
                                page = i,
                                countryCode = "DE"))
DE_Venues2_content <- fromJSON(rawToChar(DE_Venues2$content))
DE_Venues2_table[[i]] <- as_tibble(DE_Venues2_content[["_embedded"]][["venues"]])
}

# combining the resulting list by rows and extract information needed
DE_Venues3_table <- do.call(bind_rows, DE_Venues2_table)
DE_Venues3_table <- tibble(name = DE_Venues3_table$name,
                        city = DE_Venues3_table$city$name,
                        postalCode = DE_Venues3_table$postalCode,
                        address = DE_Venues3_table$address$line1,
                        url = DE_Venues3_table$url,
                        longitude = as.numeric(DE_Venues3_table$location$longitude),
                        latitude = as.numeric(DE_Venues3_table$location$latitude))

# integrating all information into one data frame
DE_Venues4_table <- bind_rows(DE_Venues3_table, DE_Venues1_table)

# take a look the final extracted information
glimpse(DE_Venues4_table)
```

#### Visualizing the extracted data
```{r message=FALSE}
# exclude Venues that are outside the Germany
DE_Venues4_table$longitude[DE_Venues4_table$longitude<5.866944 | DE_Venues4_table$longitude>15.043611] <- NA
DE_Venues4_table$latitude[DE_Venues4_table$latitude < 47.271679 | DE_Venues4_table$latitude> 55.0846] <- NA

# plot a Germany map with location of Venues
ggplot() + 
  geom_polygon(aes(x = long, y = lat, group = group), data = map_data("world", region = "Germany"), fill = "grey90",color = "black") +
  geom_point(aes(x = longitude, y = latitude), data = DE_Venues4_table) +
  theme_void() + 
  coord_quickmap() +
  labs(title = "Event locations across Germany", caption = "Source: ticketmaster.com") + theme(title = element_text(size=8, face='bold'), plot.caption = element_text(face = "italic"))
```
#### Event locations in other countries
```{r message=FALSE}
# In order to get information about clubes in Italy, one only needs to change the "countryCode" option of GET function into "IT"
IT_Venues1 <- GET("https://app.ticketmaster.com/discovery/v2/venues",
                    query =list(apikey = APIkey,
                                locale = "*",
                                countryCode = "IT")) 

IT_Venues1_content <- fromJSON(rawToChar(IT_Venues1$content))
IT_Venues1_table <- as_tibble(IT_Venues1_content[["_embedded"]][["venues"]])
IT_Venues1_table <- tibble(name = IT_Venues1_table$name,
                        city = IT_Venues1_table$city$name,
                        postalCode = IT_Venues1_table$postalCode,
                        address = IT_Venues1_table$address$line1,
                        url = IT_Venues1_table$url,
                        longitude = as.numeric(IT_Venues1_table$location$longitude),
                        latitude = as.numeric(IT_Venues1_table$location$latitude))
# glimpse(IT_Venues1_table)

pages <- as.numeric(IT_Venues1_content[["page"]][["totalPages"]])
IT_Venues2_table <- list()
for (i in 1:pages) {
IT_Venues2 <- GET("https://app.ticketmaster.com/discovery/v2/venues",
                    query =list(apikey = APIkey,
                                locale = "*",
                                page = i,
                                countryCode = "IT"))
IT_Venues2_content <- fromJSON(rawToChar(IT_Venues2$content))
IT_Venues2_table[[i]] <- as_tibble(IT_Venues2_content[["_embedded"]][["venues"]])
}

IT_Venues3_table <- do.call(bind_rows, IT_Venues2_table)
IT_Venues3_table <- tibble(name = IT_Venues3_table$name,
                        city = IT_Venues3_table$city$name,
                        postalCode = IT_Venues3_table$postalCode,
                        address = IT_Venues3_table$address$line1,
                        url = IT_Venues3_table$url,
                        longitude = as.numeric(IT_Venues3_table$location$longitude),
                        latitude = as.numeric(IT_Venues3_table$location$latitude))
IT_Venues4_table <- bind_rows(IT_Venues3_table, IT_Venues1_table)

#glimpse(IT_Venues4_table)

ggplot() + 
  geom_polygon(aes(x = long, y = lat, group = group), data = map_data("world", region = "Italy"), fill = "grey90",color = "black") +
  geom_point(aes(x = longitude, y = latitude), data = IT_Venues4_table) +
  theme_void() + 
  coord_quickmap() +
  labs(title = "Event locations across Germany", caption = "Source: ticketmaster.com") + theme(title = element_text(size=8, face='bold'), plot.caption = element_text(face = "italic"))

```























